TBA

### 2020-08-05 manuscript.tex

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{CJK}https://www.overleaf.com/project/5e820b28d741e00001b1ccac
\usepackage{framed}
\usepackage[hidelinks]{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}

@@

@@

\subsection{\label{sec:methods}3spn2 Model}
Quick summary of model, why we chose to use it, and interesting features.
-Compatible with lammps
-Enough resolution to deserve dynamical behavior, coarse enough to run equlibrium sims
-Previous hybridization experiments show agreement with experiments

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{CJK}
\usepackage{framed}
\usepackage[hidelinks]{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}

@@

TEST CITE \cite{Phys2014}

@@
